\bf Range Analysis for the IonMonkey JavaScript engine

### 2012-05-02 project-writings/paper.tex
charts

\author{
Ryan Pearl\footnote{Equal contribution to this work}\\
\texttt{$<$rpearl@andrew.cmu.edu$>$}\\
\and
Michael Sullivan\footnotemark[\value{footnote}]\\
\texttt{$<$mjsulliv@cs.cmu.edu$>$}\\
}

@@

A variety of other range analyses are available which formulate the problem as
a more traditional iterative dataflow problem. GCC, for example, uses an SSA
workflow algorithm due to Patterson in ``Accurate Static Branch Prediction by
Value Range Propagation.''\cite{Patterson95accuratestatic}
The orignal non-SSA based dataflow algorithm is by
Harrison in ``Compiler Analysis of the Value Ranges of Variables.''\cite{Harrison}

@@

>>>>

\author{
Ryan Pearl\\
\texttt{$<$rpearl@andrew.cmu.edu$>$}\\
\and
Michael Sullivan\\
\texttt{$<$mjsulliv@cs.cmu.edu$>$}\\
}

@@

A variety of other range analyses are available which formulate the problem as
a more traditional iterative dataflow problem. GCC, for example, uses an SSA
workflow algorithm due to Patterson in ``Accurate Static Branch Prediction by
Value Range Propagation.'' The orignal non-SSA based dataflow algorithm is by
Harrison in ``Compiler Analysis of the Value Ranges of Variables.''

@@

\begin{figure*}[!ht]
\centering
\includegraphics[width=0.98\textwidth]{counts_graph.png}
\caption{Percentage of add overflow checks eliminated}
\label{fig:count}
\end{figure*}
